Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-23 tex/main/manuscript.tex
修正图的位置和图例

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regime.
		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
		\textbf{C,} changes of water utilization pattern index.
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress, which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}A and Figure~\ref{fig:dimensions}D).   
% 1. 水资源丰富，耗水量少且灵活用水
In the P1, natural surface water resources were rather abundant with lesser water consumptions (supplementary Fig. S1 and S3) and most of which were flexible water utilization (supplementary Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but most of which built in P1 (supplementary Fig. S5 and supplementary Table S1). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
	\caption{
		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
		\textbf{A.} Total irrigated area and water consumption per unit of irrigated area.
		\textbf{B.} Gross values added of industry and services, and their water use density (WUI) respectively.
		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time. Red ones denote hub reservoirs in the basin, which plays a role in integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. Therefore, these marked reservoirs are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

@@

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory 
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure 
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{
		Transition framework of the water utilization regime towards natural-social binary cycle.
		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Regional cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle. 
		\textbf{C. Basinal cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:framework}
\end{figure*}

>>>>

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regimes and their main contributors.
		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of water utilization tendentiousness, indicated by non-provisioning water shares.
		\textbf{C,} changes of water utilization pattern, indicated by unstandardized distribution information entropy index (see supplementary: Methods. S3 for details).
		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their contributions to changes of unstandardized SFV-index.
		\textbf{E,} Main impact water uses to water utilization tendentiousnesses, and their contributions to changes of non-provisioning water shares.
		\textbf{F,} Main impact factors to water utilization patterns, and their contributions to changes of related unstandardized distribution information entropy index (see supplementary: Methods. S3 for details).
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress, which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}A and Figure~\ref{fig:dimensions}D).   
% 1. 水资源丰富，耗水量少且灵活用水
In the P1, natural surface water resources were rather abundant with lesser water consumptions (supplementary Fig. S1 and S3) and most of which were flexible water utilization (supplementary Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but most of which built in P1 (supplementary Fig. S5 and supplementary Table S1). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
	\caption{
		Causes of water utilization regime shifts: economy growths, efficiency changes, and managements.
		\textbf{A.} Changes of total irrigated area and water consumption per unit of irrigated area.
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (see supplementary: Methods. S2 for details).
		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use, at that time. Red ones denote hub reservoirs in the basin, which plays a role in integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name are denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. Therefore, these marked reservoirs are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

@@

\subsection*{Transition Framework}

\begin{figure*}[thbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{
		Transition framework of the water utilization regime towards natural-social binary cycle.
		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Regional cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle. 
		\textbf{C. Basinal cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:framework}
\end{figure*}

% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory 
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure 
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).
